### 2014-04-11 brains-results.tex
Minial hints for the future

@@

Where in the network are arrival words, are they related to the origin word, when relying on a given semantic network?  (In other words, would a semantic word be a good predictor of the arrival of words?). 
\rk{tout un blabla sur les distances dans les substitutions.}

>>>>

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution.png}
    \caption{XXXX}
    \label{fig:timebags-evolution}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{XXXX}
    \label{fig:feature-susceptibilities}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_variations-binned.png}
    \caption{XXXX}
    \label{fig:feature-variations}
\end{figure*}

@@

\TB{Where in the network are arrival words, are they related to the origin word, when relying on a given semantic network?  (In other words, would a semantic word be a good predictor of the arrival of wrds?).}
\rk{tout un blabla sur les distances dans les substitutions.}

\rk{is this really necessary?}
